Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex

\subsubsection{Results - Heterogeneous Data Tasks}
The participants, recruited informally via word of mouth, consisted of 7 male and 1 female. They were split evenly into two age groups of 18--25 and 26--32.   
% mention # that were computer scientists here?

>>>>

\subsubsection{Results - Heterogeneous Data Tasks}

The 8 participants, recruited informally via word of mouth, consisted of 7 male and 1 female. They were split evenly into two age groups of 18-25 and 26-32.   
% mention # that were computer scientists here?
